\documentclass[12pt, a4paper]{report}
\usepackage[a4paper, left=3.5cm, right=3cm, top=3cm,bottom=3cm]{geometry}
\title{Exposé\\
	\Large{Survey on Continual Learning}}
\author{Jörg Schantz (ru23cor)}
\date{November 2024}
\begin{document}
	\maketitle
	\renewcommand{\labelenumii}{\arabic{enumi}.\arabic{enumii}}
	\renewcommand{\labelenumiii}{\arabic{enumi}.\arabic{enumii}.\arabic{enumiii}}
	\renewcommand{\labelenumiv}{\arabic{enumi}.\arabic{enumii}.arabic{enumiii}.\arabic{enumiv}}
\section*{Idea}
	The idea of this thesis is to give a good overview of the machine learning (ML) field continual learning (CL) but through the lens of a statistician. This is to be achieved by gathering various papers on the topic and breaking down their statistical foundations. These should cover a broad spectrum of the possibilities in CL e.g. the different methodologies or criteria.\\
	Since I enjoy coding and fiddling around with practical models more than their theory I could imagine training a linear continual learner with different regularization methods or something in the likes of for the last part of the thesis. But I am a little skeptical whether this is feasible or not. Over the last year I have also developed an interest in fraud analysis, but haven't had the time to really dive into this field. So I am thinking about taking this as an opportunity to educate myself and connect the two topics. Alternatively, Dr. Rodemann suggested to deeper analyze a single paper.\\
\section*{Progress of my Studies}
	Now about the current state of my studies. I started this degree in	2017 with a minor in Insurance and Risk Management. After the first year I changed my minor to computer science. I am still dealing with a couple of mental issues, hence the long duration, but I am determined to finish my degree.\\
	This semester I intend to take my last two exams in GRM and I2ML. Both courses I have previously heard and solved most exercise sheets but never taken the final exam.\\
	In my third semester I have taken the WP course "Stichprobentheorie" and in my eighth "Einführung in die Biometrie". I2ML is my last WP course that I have to pass.\\
	The BA Seminar was together with Dr. André Klima and Dr. Georg Schollmeyer in 2020. Latter supervised my project, Visualisierung von Verteilungsunsicherheiten.
\section*{Familiarization}
	I have skimmed and summarized a multitude of papers. In order to keep a good overview of all my potential sources I created a mind map which connects every paper with its over arching topic. In total I would say my familiarization process is very advanced, near completion.
\section*{Submission}
	Preferred submission date: 01/17/2015
\section*{Potential Structure}
\begin{enumerate}
	\item Introduction
	\item Framework for CL
	\item Evaluation Metrics
	\item General Approaches
	\begin{enumerate}
		\item Replay
		\item Optimization
		\item Representation
		\item Architecture
		\item Regularization
	\end{enumerate}
	\item Distribution Drift and Bayes
	\item Regularization Approaches
	\begin{enumerate}
		\item Parameter Space
		\item Function Space
	\end{enumerate}
	\item Conclusion
\end{enumerate}
\end{document}